\section*{Background}
Please submit a two-page PDF document with standard one-inch margins and 12 point font
answering the following questions: Essay 1: Please describe your prior research experience,
your goals for the AI Residency, what you are interested inworking on during the Residency,
and how the AI Residency would help you achieve your goals. In particular, please provide
a detailed description of your topics of interest. Essay 2: Describe a recent paper or project
in AI that you were excited about and why. Be specific.

\section*{Prior Research Experience}
Right now, I'm working on Neural Machine Translation for Indic Languages.

\textbf{Goal of the project:} Build a multilingual translation which can translate 

\section*{Research Project:}

Previously, I only had some ideas about Federated Learning in space recommendation systems. So, I started to look out for other directions in which we can utilize Federated Learning for enhancing the efficiency of algorithms for edge computing. While researching ideas, I came across several of your works on Federated Learning. The papers like FedNL and Guide to Federated Optimization enlightened me about the different approaches and directions. \\
\\
At Optimization and Machine Learning Lab, there is ongoing research in Federated Learning in multiple spaces like Optimization,
Communication, Generalization, and many more. I believe that under the guidance of Prof. Peter
I can learn more about these spaces in the context of Federated Learning and contribute
to the ongoing project. Which will eventually help me build a profile for my Ph.D. and
decide on a direction for it.